Conflict Driven Evolution and Urban Development: \\ Evidence from the Holy Roman Empire\footnote{ I thank Lara Andermann, Leonie Bielefeld, Daniel Bursian, Davide Cantoni, Emilio Esguerra, Filip Milojevic, Johannes Vorbach and Matthias Weigand for helpful comments and feedback. }

### 2023-06-26 paper/paper.tex
#29 begin external validity, cite CY HHE

The entire territory goes to another state (or multiple) when a ruling lineage goes extinct, but conquests usually happen one at a time. The average number of simultaneous switches is likely much larger for successions than for conquests. If conquests had an effect on construction activity not just through the change in state power but also through the number of cities that switched simultaneously, then the coefficient $\theta_{conquest}$ no longer captures only the causal effect of switching. I believe this is one of the remaining threats to the internal validity of my regression analysis. It should be possible to compute the number of cities that switch to the same state as city $i$ in period $t$ and then to control for it, which would solve the problem. I leave this for a future extension of the paper.

External validity BLANK
Switches barely explain variation in construction activity (super low within-R2) - possible solution: add lags for controls BLANK

>>>>

An entire territory goes to another state (or multiple) when a ruling lineage goes extinct, but conquests usually happen one at a time. The average number of simultaneous switches is likely much larger for successions than for conquests. If conquests had an effect on construction activity not just through the change in state power but also through the number of cities that switched simultaneously, then the coefficient $\theta_{conquest}$ no longer captures only the causal effect of switching. I believe this is one of the remaining threats to the internal validity of my regression analysis. It should be possible to compute the number of cities that switch to the same state as city $i$ in period $t$ and then to control for it in Equation \ref{eq:baseline}, which would solve the problem. I leave this for a future extension of this paper.

Having discussed issues with internal validity now, I will briefly talk about external validity. For this purpose it is helpful to first put the goal of my paper into context. 
\cite{cantoni2021}

I doubt that we can learn anything about present conflicts or present growth rates from my results.

In terms of \cite{levine2021, levine2022}'s model of state systems, most international conflict nowadays is defined by the presence of multiple extremely strong outsiders who act to keep the balance of power in the status quo.
